\TITLE

### 2024-08-12 paper/main.tex
update fairnesss section

\subsection{Dispute Resolution System}
\label{sec:dispute-resolution}
\begin{sloppypar}
Disputes are common in transactions, and systems are needed to ensure that rules and laws are followed. Traditionally, this has involved legal contracts and law enforcement. With blockchain technology, smart contracts offer a new way by putting the details of a contract into code and enforcing it through a consensus mechanism.~\cite{allenGovernanceBlockchainDispute2019}.
\end{sloppypar}

\begin{sloppypar}
One challenge with blockchain is dealing with external information, which is where \textit{oracles} come in. They feed real-world data into the blockchain~\cite{breidenbachChainlinkNextSteps2021}. This is important for dispute resolution systems like Themis~\cite{mengThemisDecentralizedEscrow2019} and Kleros~\cite{bergollaKlerosSociolegalCase2022}, which use decentralized networks to make fair decisions. However, these systems may struggle with complex disputes that require special knowledge and privacy.
\end{sloppypar}

@@

Blockchain-based dispute resolution platforms such as  Kleros~\cite{bergollaKlerosSociolegalCase2022, nappertDecentralizedJusticeReinventing2020, gudkovCrowdArbitrationBlockchain2020}, Themis~\cite{mengThemisDecentralizedEscrow2019}, Aragon Court~\cite{AragonWhitepaper2023,aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution (ODR) systems~\cite{allenGovernanceBlockchainDispute2019, lingwallShouldCodeBe2019} offer a promising direction. These systems could employ a pool of field experts who, in the event of a dispute, would examine the smart contract, the proofs ( $\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$) and provide verdicts. Expert participation and honest verdicts are encouraged through a system of fees, stakes and rewards. At the time of writing Kleros is the most successful platform for resolving consumer disputes in e-commerce or collaborative economy. It has received funding from the Commission's European Innovation Council~\cite{CommissionEuropeanInnovation2020}. The protocol claims to have resolved 1645 disputes, employing 716 jurors and rewarding them with 401 ETH. Kleros allows integration with new protocols and we leave it to future work.

>>>>

\subsection{Dispute Resolution System}
\label{sec:dispute-resolution}
\begin{sloppypar}
Disputes are common in transactions, and systems are needed to ensure that rules and laws are followed. Traditionally, this has involved legal contracts and law enforcement. With blockchain technology, smart contracts offer a new way by putting the details of a contract into code and enforcing it through a consensus mechanism.~\cite{allenGovernanceBlockchainDispute2019,lingwallShouldCodeBe2019}.
\end{sloppypar}

\begin{sloppypar}
One challenge with blockchain is dealing with external information, which is where \textit{oracles} come in. They feed real-world data into the blockchain~\cite{breidenbachChainlinkNextSteps2021}. This is important for dispute resolution systems like Kleros~\cite{bergollaKlerosSociolegalCase2022, nappertDecentralizedJusticeReinventing2020, gudkovCrowdArbitrationBlockchain2020} or Themis~\cite{mengThemisDecentralizedEscrow2019}, which use decentralized networks to make fair decisions. Such arbitration services employ a pool of local experts who would
In the event of a dispute, they would examine the smart contract and all the evidence to provide verdicts back to the blockchain. The SP would be required to lock a certain amount of funds into the protocol, which would be cut in the event of misbehaviour. However, these systems may struggle with complex disputes that require specialised knowledge and privacy.
\end{sloppypar}

@@

Blockchain-based dispute resolution platforms such as  Kleros~\cite{bergollaKlerosSociolegalCase2022, nappertDecentralizedJusticeReinventing2020, gudkovCrowdArbitrationBlockchain2020}, Themis~\cite{mengThemisDecentralizedEscrow2019}, Aragon Court~\cite{AragonWhitepaper2023,aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution (ODR) systems~\cite{allenGovernanceBlockchainDispute2019, lingwallShouldCodeBe2019} offer a promising direction. These systems could employ a pool of field experts who, in the event of a dispute, would examine the smart contract, the proofs ( $\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$) and provide verdicts. Expert participation and honest verdicts are encouraged through a system of fees, stakes and rewards. At the time of writing Kleros is the most successful platform for resolving consumer disputes in e-commerce or collaborative economy. It has received funding from the Commission's European Innovation Council~\cite{CommissionEuropeanInnovation2020}. The protocol claims to have resolved 1645 disputes, employing 716 jurors and rewarding them with 401 ETH~\cite{KlerosHomepage}. Kleros allows integration with new protocols and we leave it to future work.
